Pretty darn good control: when are approximate solutions better than approximate models

### 2023-01-17 manuscript/manuscript.Rmd
mini
changes to how models are presented

In this section we introduce some models describing the population dynamics of fisheries.
In general, the class of models that appear in this context are *first order finite difference equations*.
For $n$ species, these models have the general form
\begin{align}
  \label{eq:general model}
  N_{t+1} - N_t = f(N_t) - h_t,
\end{align}
where $N(t) = (A_t,\ B_t,\ \dots) \in \mathbb{R}^{n}_+$ is a vector of populations, $f:\mathbb{R}^{n}\to\mathbb{R}^{n}$ is an arbitrary function, and $h_t$ is the harvest size at timestep $t$.

## Single species models

Most commonly, fisheries use 1-dimensional models, $n=1$.
One such model appearing in a variety of ecological contexts is *logistic growth*, for which
$$
  f(N_t) = r N_t\big(1 - N_t / K \big) =: L(N_t).
$$
More relevant to our current work, is the following single-species model studied in \cite{may77},
\begin{align}
  \label{eq:may}
  N_{t+1} - N_t
  = L(N_t) - \frac{\beta H N_t^2}{c^2 + N_t^2}.
\end{align}
The model has five parameters: a constant population $H$ of a species which preys on $N$, the maximal rate of predation $\beta$, and the predation half-maximum biomass $c$.

Part of what makes eq. \eqref{eq:may} an interesting study case is the presence of a *tipping point* (see Fig. \ref{tbd}).
Holding the value of $\beta$ fixed, for intermediate values of $H$ there exist two stable fixed points for the state $V_1$ of the system, these two attractors separated by an unstable fixed point.
At a certain threshold value of $H$, however, the top stable fixed point collides with the unstable fixed point and both are annihilated.
For this value of $H$, and for higher values, only the lower fixed point remains.

@@

>>>>

In this section we introduce some models describing the population dynamics of fisheries.
In general, the class of models that appear in this context are *first order finite difference equations*.
For $n$ species, these models have the general form
\begin{align}
  \label{eq:general model}
  N_{t+1} - N_t = f(N_t) - h_t := N_t,
\end{align}
where $N_t = (X_t,\ Y_t,\ \dots) \in \mathbb{R}^{n}_+$ is a vector of populations, $f:\mathbb{R}^{n}\to\mathbb{R}^{n}$ is an arbitrary function, and $h_t$ is the harvest size at timestep $t$.

## A single species model

Most commonly, fisheries use 1-dimensional models, $n=1$.
One such model appearing in a variety of ecological contexts is *logistic growth*, for which
$$
  f(N_t) = r N_t\big(1 - N_t / K \big) =: L(N_t;\ r, K).
$$
More relevant to our current work, is the following single-species model studied in \cite{may77},
\begin{align}
  \label{eq:may}
  N_{t+1} - N_t
  = L(N_t) - F(N_t, H; \beta,c),
\end{align}
where,
\begin{align*}
  F(N,H;\ \beta,c) := \frac{\beta H N^2}{c^2 + N^2}.
\end{align*}
The model has five parameters: a constant population $H$ of a species which preys on $N$, the maximal rate of predation $\beta$, and the predation half-maximum biomass $c$.

Eq. \eqref{eq:may} is an interesting study case of a *tipping point* (see Fig. \ref{tbd}).
Holding the value of $\beta$ fixed, for intermediate values of $H$ there exist two stable fixed points for the state $V_1$ of the system, these two attractors separated by an unstable fixed point.
At a certain threshold value of $H$, however, the top stable fixed point collides with the unstable fixed point and both are annihilated.
For this value of $H$, and for higher values, only the lower fixed point remains.

@@

Consider the following three species *generalization* of eq. \eqref{eq:may}:
\begin{align}
  \label{eq:may 3d}
  \Delta X_t = L(X_t; r_X, K_X)
\end{align}
